Outputs - civil servants' survey

### 2024-12-06 reports/paper_outputs_Dec_2024.qmd
Update SEM models

sjPlot::tab_model(politicization_mod1,influence_mod1,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = c("Expected politicization","Expected influence"),
                  order.terms = c(2:4,1))

@@

sjPlot::tab_model(exit_mod1,exit_mod2,
                  voice_mod1,voice_mod2,
                  work_mod1,work_mod2,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
                  order.terms = c(2,5:6,3:4,7:8,1))

@@

```{r}
SEM_All <-'

##Direct effects##
INTENT_EXIT_2 ~ cp_ex*BACKSLIDING_2
PROJECT_VOICE ~ cp_vc*BACKSLIDING_2 + PAST_VOICE
PROJECT_EFFORT ~ cp_eff*BACKSLIDING_2 + PAST_EFFORT

##Mediators##
PROJECT_POLITICIZATION ~ a1*BACKSLIDING_2 + PAST_POLITICIZATION 
PROJECT_INFLUENCE ~ a2*BACKSLIDING_2 + PAST_INFLUENCE

INTENT_EXIT_2 ~ b1_ex*PROJECT_POLITICIZATION + PAST_POLITICIZATION
INTENT_EXIT_2 ~ b2_ex*PROJECT_INFLUENCE + PAST_INFLUENCE

PROJECT_VOICE ~ b1_vc*PROJECT_POLITICIZATION + PAST_POLITICIZATION
PROJECT_VOICE ~ b2_vc*PROJECT_INFLUENCE + PAST_INFLUENCE

PROJECT_EFFORT ~ b1_eff*PROJECT_POLITICIZATION + PAST_POLITICIZATION
PROJECT_EFFORT ~ b2_eff*PROJECT_INFLUENCE + PAST_INFLUENCE

@@

##Other correlations##
PROJECT_POLITICIZATION~~PAST_INFLUENCE
PROJECT_INFLUENCE~~PAST_POLITICIZATION
PAST_POLITICIZATION~~PAST_INFLUENCE
PAST_EFFORT~~PROJECT_POLITICIZATION
PAST_EFFORT~~PROJECT_INFLUENCE

@@

@@

@@

>>>>

sjPlot::tab_model(politicization_mod1,influence_mod1,
                  show.est = F,
                  show.ci = F,
                  show.se = F,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = c("Expected politicization","Expected influence"),
                  order.terms = c(2:4,1))

@@

sjPlot::tab_model(exit_mod1,exit_mod2,
                  voice_mod1,voice_mod2,
                  work_mod1,work_mod2,
                  show.est = F,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
                  order.terms = c(2,5:6,3:4,7:8,1))

@@

```{r}
SEM_All <-'
##latent variables##
Past_influence=~ Q4_1 + Q4_2 + Q4_3
Past_politicization=~ Q10_1 + Q10_2 + Q10_3
Demo_backsliding=~ Q16_1 + Q16_2 + Q16_3 + Q16_4 + Q16_5 + Q15
Past_voice=~Q22_1+Q22_2+Q22_3
Past_effort=~PAST_EFFORT

##Direct effects##
INTENT_EXIT_2 ~ cp_ex*Demo_backsliding
PROJECT_VOICE ~ cp_vc*Demo_backsliding + Past_voice
PROJECT_EFFORT ~ cp_eff*Demo_backsliding + Past_effort

##Mediators##
PROJECT_POLITICIZATION ~ a1*Demo_backsliding + Past_politicization 
PROJECT_INFLUENCE ~ a2*Demo_backsliding + Past_influence

INTENT_EXIT_2 ~ b1_ex*PROJECT_POLITICIZATION + Past_politicization
INTENT_EXIT_2 ~ b2_ex*PROJECT_INFLUENCE + Past_influence

PROJECT_VOICE ~ b1_vc*PROJECT_POLITICIZATION + Past_politicization
PROJECT_VOICE ~ b2_vc*PROJECT_INFLUENCE + Past_influence

PROJECT_EFFORT ~ b1_eff*PROJECT_POLITICIZATION + Past_politicization
PROJECT_EFFORT ~ b2_eff*PROJECT_INFLUENCE + Past_influence

@@

##Other correlations##
PROJECT_POLITICIZATION~~Past_influence
PROJECT_INFLUENCE~~Past_politicization
Past_politicization~~Past_influence
Past_effort~~PROJECT_POLITICIZATION
Past_effort~~PROJECT_INFLUENCE

@@

```{r}
standardizedSolution_boot_ci(fit_all) %>% 
  #filter(op==":=") %>% 
  dplyr::select(label,est.std,boot.ci.lower,boot.ci.upper,pvalue) %>% 
  mutate(across(2:4, round, 2)) %>% 
  mutate(across(5, round, 3)) %>% 
  gt::gt()
```

@@

```{r}
fitmeasures(fit_all, c('chisq','df','pvalue','cfi','tli', 'rmsea', 'rmsea.ci.upper','rmsea.ci.lower', 'srmr')) %>% 
  broom::tidy() %>% 
  pivot_wider(names_from = names,values_from = x) %>% 
  mutate(chisq_01 = str_c(chisq %>% round(3)," [","df=",df,", p=",pvalue %>% round(3),"]"),
         rmsea_01 = str_c(rmsea %>% round(3)," CI[", rmsea.ci.lower %>% round(3),",",rmsea.ci.upper %>% round(3),"]"),
         cfi = cfi %>% round(3),
         tli = tli %>% round(3),
         srmr = srmr %>% round(3),
         n = fit_all@SampleStats@nobs) %>%
  dplyr::select('N' = n,
          'Chi-sq' = chisq_01,
         'CFI' = cfi,
         'TLI' = tli,
         'RMSEA' = rmsea_01,
         'SRMR' = srmr) %>% 
  t() %>% 
  kableExtra::kable()
```

@@

```{r, fig.width=8,fig.height=6}
p1<- cars %>% ggplot(aes(x=speed))+ geom_histogram()

p1

#ggsave("p1.jpg",width = 8, height = 4,dpi=600)
```
